% Pandoc/Quarto template for den-paper extension
\documentclass[
  manuscript=article,
  layout=publish,
  year=2026,
  volume=1,
]{den}

% DOI

% Conference (for proceedings/poster)

% Dates
\published{20 May 2026}

% Editor and reviewers

% Strip abstract fields from bibliography entries (prevents LuaLaTeX parsing issues)

% Title
\title{User Guide for the DEN Paper Template}

% Authors and affiliations
\author{First Author \orcid{0000-0000-0000-0000}}
\affiliation{Institution-1, City, Country}
\email{correspondence@email.domain}
\author{Krisna Gupta \orcid{0000-0001-8695-8514}}
\affiliation{Institution-2, City, Country}
\author{Third Author}
\affiliation{Institution-3, City, Country}

% Keywords
\keywords{keyword; keyword-two; keyword number three}

% JEL classification codes
\jel{C22, O47}

% Abbreviations

% Pandoc/Quarto compatibility macros
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\providecommand{\citeproc}[2]{#1}
\providecommand{\citeproctext}{}

% Support for graphics
\RequirePackage{graphicx}

% Support for ding symbols (checkmarks, etc.)
\RequirePackage{pifont}

% Support for table column width calculations (required by Quarto-generated tables)
\RequirePackage{calc}

% Pandoc image handling - required for newer Pandoc/Quarto versions
% Constrains images to text width to prevent overflow
\makeatletter
\providecommand{\pandocbounded}[1]{%
  \sbox0{#1}%
  \ifdim\wd0>\linewidth
    \resizebox{\linewidth}{!}{#1}%
  \else
    #1%
  \fi
}
\makeatother

% CSL references support
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\makeatletter
\newcommand{\CSLNoBibLabel}{\renewcommand{\@biblabel}[1]{}}
\makeatother
\newenvironment{CSLReferences}[2]
 {\begin{list}{}%
  {\setlength{\leftmargin}{0pt}
   \setlength{\itemindent}{0pt}
   \setlength{\itemsep}{#2\baselineskip}
   \setlength{\parsep}{0pt}
   \setlength{\topsep}{0pt}
   \setlength{\partopsep}{0pt}
   \ifodd #1
     \setlength{\leftmargin}{\cslhangindent}
     \setlength{\itemindent}{-\cslhangindent}
   \fi}
  \CSLNoBibLabel}
 {\end{list}}

% Header includes
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Daftar Isi}
\else
  \newcommand\contentsname{Daftar Isi}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{Daftar Gambar}
\else
  \newcommand\listfigurename{Daftar Gambar}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{Daftar Tabel}
\else
  \newcommand\listtablename{Daftar Tabel}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Gambar}
\else
  \newcommand\figurename{Gambar}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Tabel}
\else
  \newcommand\tablename{Tabel}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Daftar}
\newcommand*\listoflistings{\listof{codelisting}{Daftar Daftar}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

% Keep internal links clickable without PDF border underlines.
\hypersetup{pdfborder={0 0 0}}

% Source note environment for figure attributions (right-aligned, compact)
\newenvironment{source}{%
  \vspace{-1em}%
  \begin{flushright}\scriptsize\itshape
}{%
  \end{flushright}%
}
\newcommand{\sumber}[1]{%
  \vspace{-1em}%
  \begin{flushright}\scriptsize\itshape
  Sumber: #1
  \end{flushright}%
}

% Allow LaTeX more flexibility in line breaking to prevent overflow
% (needed for Indonesian/non-English text on narrow B5 paper)
\tolerance=1000
\emergencystretch=1.5em

\begin{document}

\begin{abstract}
An abstract summarizes, in one paragraph of 300 words or fewer, the
major aspects of the entire paper. It should include: 1) the overall
purpose of the study and the research problem you investigated; 2) the
basic design of your research approach; 3) major findings as a result of
your analysis; and 4) a brief summary of your interpretations and
conclusions.
\end{abstract}

\section{User Guide for This
Template}\label{user-guide-for-this-template}

Use this template with Quarto markdown (qmd). For more information on
Quarto, visit \url{https://quarto.org}
\href{https://quarto.org/docs/authoring/markdown-basics.html\#footnotes}{here}.

\subsection{Title}\label{title}

The title should be in Title Case. Keep it concise and informative,
ideally within 12 words. Avoid abbreviations in the title unless they
are widely recognized.

\subsection{References}\label{references}

Add your bibliography entries to \texttt{ref.bib} and cite them using
standard Quarto citation syntax. Here is an example citation on diamond
open access (Fuchs dan Sandoval 2013). According to Fuchs dan Sandoval
(2013), diamond open access model is amazing.

\subsection{Footnotes}\label{footnotes}

Use footnotes sparingly. They should be used for additional information
that is not essential to the main text.\footnote{This is an example
  footnote.}

\subsection{Tables}\label{tables}

Use standard markdown tables or Quarto's table syntax.
Tabel~\ref{tbl-example} shows an example.

\begin{longtable}[]{@{}lll@{}}
\caption{Example table}\label{tbl-example}\tabularnewline
\toprule\noalign{}
\textbf{Parameter} & \textbf{Notation} & \textbf{Remarks} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\textbf{Parameter} & \textbf{Notation} & \textbf{Remarks} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
name & - & engine common identifier \\
manufacture & - & name of the manufacturer \\
bpr & \(\lambda\) & bypass ratio \\
pr & - & pressure ratio \\
thrust & \(T_0\) & maximum static thrust \\
\end{longtable}

\subsection{Figures}\label{figures}

Use standard Quarto figure syntax with
\texttt{!{[}caption{]}(path)\{\#fig-id\ width=X\%\}}. Place images in a
\texttt{fig/} folder.

\subsection{Equations}\label{equations}

Use standard LaTeX equation syntax. Persamaan~\ref{eq-cauchy} shows an
example equation.

\begin{equation}\protect\phantomsection\label{eq-cauchy}{
\rho\frac{\mathrm{D} \mathbf{u}}{\mathrm{D} t} = - \nabla p + \nabla \cdot \boldsymbol \tau + \rho\,\mathbf{g}
}\end{equation}

\section{Sections}\label{sections}

Organize your paper using standard markdown headings.

Some standard sections are:

\begin{itemize}
\tightlist
\item
  Introduction
\item
  Methods
\item
  Results
\item
  Discussion
\item
  Conclusion
\end{itemize}

\section*{Acknowledgement}\label{acknowledgement}
\addcontentsline{toc}{section}{Acknowledgement}

Include your acknowledgements in this section.

\section*{Funding Statement}\label{funding-statement}
\addcontentsline{toc}{section}{Funding Statement}

When applicable, please specify the funding information for this
research.

\section*{Reproducibility Statement}\label{reproducibility-statement}
\addcontentsline{toc}{section}{Reproducibility Statement}

\textbf{Mandatory section!}

\subsection{Information on how to reproduce this research, including
access to: 1) source code related to the research, 2) source code for
the figures, 3) source code/data for the tables when
applicable.}\label{information-on-how-to-reproduce-this-research-including-access-to-1-source-code-related-to-the-research-2-source-code-for-the-figures-3-source-codedata-for-the-tables-when-applicable.}

\section{Pendahuluan}\label{pendahuluan}

\section{Studi Literatur}\label{studi-literatur}

xxxx

\section{Metodologi}\label{metodologi}

\subsection{Data}\label{data}

\subsection{Metode}\label{metode}

\section*{Analisis}\label{analisis}
\addcontentsline{toc}{section}{Analisis}

\protect\phantomsection\label{refs}
\begin{CSLReferences}{1}{1}
\bibitem[\citeproctext]{ref-fuchs2013diamond}
Fuchs, Christian, dan Marisol Sandoval. 2013. {``The diamond model of
open access publishing: Why policy makers, scholars, universities,
libraries, labour unions and the publishing world need to take
non-commercial, non-profit open access serious.''} \emph{TripleC:
Communication, capitalism \& critique} 11 (2): 428--443.

\end{CSLReferences}

\end{document}
